Demystifying the Computer Science Ph.D. Admission in \\US Universities\\{\Large A guide for Vietnamese and International Students

### 2023-06-11 phd-cs-us.tex
updates

\newcommand{\mycomment}[3][\color{black}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{Demystifying the Computer Science Ph.D. Admission in the US \\{\Large A guide for Vietnamese and International Students}}
\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen}, \href{https://cs.gmu.edu}{George Mason University}}
%\setcounter{secnumdepth}{3}
\begin{document}
\maketitle

@@

So I want to share my opinions and advice for those who are interested in applying for a \textbf{PhD in Computer Science in the US}.
While I wrote this document for Vietnamese students interested in CS, it should be applicable to students in various countries interested in STEM.
Moreover, while many examples given are for GMU, which is 32rd in the US according CSRankings (see \S\ref{sec:ranking}), the writing should be generalize to most other R1\footnote{An \href{https://en.wikipedia.org/wiki/List_of_research_universities_in_the_United_States}{R1 institution} in the US is a research-intensive university with a high level of research activity across various disciplines.} universities  (though \emph{very} top schools might be very extreme, e.g., see the admission process at \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{CMU}).

@@

        Also do not use Mr. or Mrs., or just write Firstname. May be it is OK with others but I find it a bit disrespectful. As you know that prof. better and depends on their preference, you can call them by their Firstname.

>>>>

\newcommand{\mycomment}[3][\color{black}]{{#1{{#2}: {#3}}}}
\newcommand{\tvn}[1]{\mycomment{TVN}{#1}}{}
\newcommand{\tl}[1]{\mycomment{ThanhLe}{#1}}{}
\newcommand{\red}[1]{{\color{red}{#1}}}
\renewcommand{\figurename}{Fig.}
\renewcommand{\tablename}{Tab.}
\title{Demystifying the Computer Science Ph.D. Admission in \\US Universities\\{\Large A guide for Vietnamese and International Students}}
\date{\today}
\author{\small \href{https://nguyenthanhvuh.github.io}{ThanhVu (Vu) Nguyen}, \href{https://cs.gmu.edu}{George Mason University}}
%\setcounter{secnumdepth}{3}
\begin{document}
\maketitle

@@

So I want to share my opinions and advice for those who are interested in applying for a \textbf{PhD in Computer Science in the US}.
While I wrote this document for Vietnamese students interested in CS, it should be applicable to students in various countries.
Moreover, while many examples given are for GMU, which is 32nd in the US according CSRankings (see \S\ref{sec:ranking}), the writing should be generalize to most other R1\footnote{An \href{https://en.wikipedia.org/wiki/List_of_research_universities_in_the_United_States}{R1 institution} in the US is a research-intensive university with a high level of research activity across various disciplines.} universities  (though \emph{very} top schools is much more selective, e.g., see the admission process at \href{https://da-data.blogspot.com/2015/03/reflecting-on-cs-graduate-admissions.html}{CMU}).

@@

 \item If you don't know the prof., do not use Mr. or Mrs., or Firstname. To me it seems a bit disrespectful. As you know that prof. better and depends on their preference, you can call them by their Firstname.
